---
title: "Performing queries on the 'poisson' API"
author: "Benoit Richard, Pascal Irz & David Dorchies"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example_niveaux_nappes_api}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "70%",
  fig.align = "center"
)
#load(system.file("vignettes/example_niveaux_nappes_api.RData", package = "hubeau"))
```

This vignette shows how to use the [`hubeau` R package](https://github.com/inrae/hubeau) in order to retrieve data of river electrofishing surveys carried out by the French Biodiversity Agency ([OFB](https://www.ofb.gouv.fr/)) and their partners from the [API "Poisson"](https://hubeau.eaufrance.fr/page/api-poisson) of the [Hub'eau](https://hubeau.eaufrance.fr/) portal. 

The data includes observations, indicators, operations and sampling sites, which are stored in the ASPE (“Application de Saisie des données Piscicoles et Environnementales”) database administrated by the French Biodiversity Agency. A more precise description of the ASPE database may be found in Irz *et al.* (2022).

> Irz P, Vigneron T, Poulet N, Cosson E, Point T, Baglinière E, Porcher JP. 2022. A long-term monitoring database on fish and crayfish species in French rivers. *Knowl. Manag. Aquat. Ecosyst.* 423, 25, [DOI:10.1051/kmae/2022021](https://doi.org/10.1051/kmae/2022021).

We illustrate the use of this API for the departement of Calvados (`code_departement=14`) with some example of maps and charts useful for the interpretation of these data.

```{r}
my_dept <- "14"
```

# Getting started

# Retrieving the data

## Sites

## Surveys

## Observations





